Computing environment

### 2024-12-12 analysis/environment.qmd
Dockerization!

```{r}
#| class-output: sh
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
```

>>>>

```{r}
#| class-output: sh
makevars_path <- file.path(Sys.getenv("HOME"), ".R/Makevars")

if (file.exists(makevars_path)) {
  writeLines(readLines(makevars_path))
} else {
  message("No .R/Makevars on the computer that built this")
}
```
